% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% CV.tex
%% <https://github.com/zachscrivena/simple-resume-cv>
%% This is free and unencumbered software released into the
%% public domain; see <http://unlicense.org> for details.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info (to be customized).
\newcommand{\CVAuthor}{Victor Hieu Nguyen}
\newcommand{\CVTitle}{Victor Hieu Nguyen's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://vhi3u.github.io/}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
Charlotte, NC
\par
\href{mailto:vhieu@unc.edu}
{vhieu@unc.edu}
\,\SubBulletSymbol\,
+1\,(704)\,877-6570
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\textbf{Georgia Institute of Technology},
Atlanta, GA

\Gap
Ph.D. in
Ocean Science and Engineering
\hfill
Incoming \DatestampYMD{2026}{08}{21}

\BigGap
\Entry
\textbf{University of North Carolina at Chapel Hill},
Chapel Hill, NC

\Gap
Environmental Science, B.S., Applied Mathematics, B.S.
\hfill
\DatestampYMD{2022}{08}{15} --
\DatestampYMD{2026}{05}{09}
\BulletItem
Honors Carolina Laureate
\BulletItem
Highest Honors Designation
\BulletItem
Carolina Research Scholar
\BulletItem
Thesis: \textit{Shoal Bathymetry Influence on Offshore Transport and Mixing}
\BulletItem
Minor: Marine Sciences

%%%%%%%%%%%%%%%%%%%%%%%%%
%% RESEARCH EXPERIENCE %%
%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Experience}
{Experience}
{PDF:ResearchExperience}

\Entry
{\textbf{Georgia Institute of Technology}},
Atlanta, GA

\Gap
Graduate Research Assistant\hfill
Incoming \DatestampYMD{2026}{08}{21}
\BulletItem
Georgia Tech Oceanography Group
\BulletItem
 Advisor:
Prof.~Lilian~Dove

\Gap
\Entry
{\textbf{University of North Carolina at Chapel Hill}},
Chapel Hill, NC

\Gap
Undergraduate Research Assistant\hfill
\DatestampYMD{2025}{07}{01} --
Present
\BulletItem
Carolina Dynamical Oceanography Group
\BulletItem
Offshore transport and mixing in Diamond Shoals using Oceananigans
\BulletItem
Advisor:
Prof.~Ken~Zhao

\Gap
\Entry
{\textbf{University of North Carolina at Chapel Hill}}, Chapel Hill, NC

\Gap
Undergraduate Research Assistant \hfill
\DatestampYMD{2023}{03}{01} --
\DatestampYMD{2026}{05}{09}
\BulletItem
Seim Lab for Observational Physical Oceanography
\BulletItem
Hydrgraphic variability of Cape Hatteras coastal region using Slocum gliders
\BulletItem
Advisor:
Prof.~Harvey~Seim

\Gap
\Entry
\textbf{SECOORA}, Remote

\Gap
Data Engineering Intern \hfill
\DatestampYMD{2025}{05}{01} --
\DatestampYMD{2025}{08}{01}
\BulletItem
SECOORA Slocum Data Processing and Management Framework (SDPMF) for Slocum gliders
\BulletItem
Advisor(s): Prof. ~Harvey~Seim, Prof. ~Catherine~Edwards

\Gap
Underwater Glider Pilot \hfill
\DatestampYMD{2023}{07}{01} --
\DatestampYMD{2025}{11}{01}
\BulletItem
Glider data used for hurricane forecasting
\BulletItem
Advisor(s): Prof. ~Harvey~Seim, Prof. ~Catherine~Edwards, Karen Dreger

\Gap
\Entry
{\textbf{Texas A\&M University}}, College Station, TX

\Gap
Summer REU Fellow \hfill
\DatestampYMD{2024}{05}{01} --
\DatestampYMD{2024}{08}{01}
\BulletItem
Carbon Cycle and Earth Environment Lab
\BulletItem
Long-term impact of carbon dioxide removal methods on ocean and atmospheric tracers
\BulletItem
Advisor(s):
Prof.~Shuang~Zhang, Shihan Li


%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% AWARDS & SCHOLARSHIPS %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Awards \&\newline
Scholarships}
{Awards \& Scholarships}
{PDF:AwardsAndScholarships}

\textbf{National Science Foundation Graduate Research Fellowship}
\hfill
\DatestampY{2026} --
\DatestampY{2031}
\BulletItem
Annual award: \$37,000

\Gap
\textbf{Epsilon Eta Honors Environmental Fraternity}
\hfill
\DatestampYMD{2024}{03}{01}

\Gap
\textbf{Dean's List}
\hfill
\DatestampYMD{2022}{08}{01} -- 
\DatestampYMD{2026}{05}{09}
\BulletItem
Fall 2022, Spring 2023, Spring 2024, Spring 2026

%%%%%%%%%%%%%%%%%%%
%% PRESENTATIONS %%
%%%%%%%%%%%%%%%%%%%

\Section
{Presentations}
{Presentations}
{PDF:Presentations}

\Entry
\textbf{Nguyen, V.H.}, Zhao, K.X., and Seim, H. (2026). \textit{Oral Presentation}. Shoal Influence on Offshore Flow and Mixing. Earth, Marine, and Environmental Sciences Celebration of Research Symposium, UNC.

\Gap
\Entry
\textbf{Nguyen, V.H.} and Seim, H. (2025). \textit{Poster Presentation}. Shelf Water Mixing from Cape Hatteras Coastal Region: Tropical Cyclone and Winter Storm Effect on Destratification. AGU25 Annual Meeting, American Geophysical Union.

\Gap
\Entry
\textbf{Nguyen, V.H.} and Seim, H. (2025). \textit{Poster Presentation}. Continental shelf hydrographic variability during the Processes driving Exchange at Cape Hatteras (PEACH) program. Celebration of Undergraduate Research, UNC.

\Gap
\Entry
Zhang, S., \textbf{Nguyen, V.H.}, et al. (2024). \textit{Poster Presentation}. Long-term carbon storage capacity and ocean co-benefits of carbon dioxide removal methods. AGU24 Annual Meeting, American Geophysical Union.

\Gap
\Entry
Seim, H., Edwards, C., and \textbf{Nguyen, V.H.} (2024). \textit{Poster Presentation}. Southern Mid-Atlantic Bight conditions observed with shelf gliders during the PEACH project during 2017-2018. NSF OOI Community Workshop: Pioneer Array, Old Dominion University.

\Gap
\Entry
\textbf{Nguyen, V.H.}, Zhang, S., and Li, S. (2024). \textit{Oral Presentation}. Carbon capture potential and ocean system interactions. Department of Oceanography REU Symposium, TAMU.

\Gap
\Entry
\textbf{Nguyen, V.H.}, Zhang, S., and Li, S. (2024). \textit{Poster Presentation}. Carbon capture potential and ocean system interactions. LAUNCH REU Poster Symposium, TAMU.

\Gap
\Entry
\textbf{Nguyen, V.H.} and Seim, H. (2024). \textit{Poster Presentation}. Characterization of Hatteras Front using glider deployments from PEACH project. Celebration of Undergraduate Research, UNC.

\Gap
\Entry
\textbf{Nguyen, V.H.} and Seim, H. (2024). \textit{Poster Presentation}. Characterization of Hatteras Front using glider deployments from PEACH project. Earth, Marine, and Environmental Sciences Research Symposium, UNC.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PROFESSIONAL AFFILIATIONS & ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \Section
% {Professional Affiliations\newline
% \& Activities}
% {Professional Affiliations \& Activities}
% {PDF:ProfessionalAffiliationsActivities}

% \Entry
% {\textbf{American Geophysical Union}}
% \Gap
% \BulletItem
% Member
% \hfill
% \DatestampY{2025} --
% Present


%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Service and Outreach}
{Service and Outreach}
{PDF:ServiceAndOutreach}

\Entry
{\textbf{Carolina Science Olympiad}},
Chapel Hill, NC

\Gap
Senior Advisor
\hfill
\DatestampYMD{2025}{05}{15} --
\DatestampYMD{2026}{05}{15}
\Gap
President
\hfill
\DatestampYMD{2024}{05}{15} --
\DatestampYMD{2025}{05}{15}
\Gap
Service Chair
\hfill
\DatestampYMD{2023}{05}{15} --
\DatestampYMD{2024}{05}{15}
\Gap
Media Chair
\hfill
\DatestampYMD{2022}{10}{15} --
\DatestampYMD{2023}{05}{15}

\Entry
{\textbf{Epsilon Eta Honors Environmental Fraternity}}
Chapel Hill, NC

\Gap
Academic Chair
\hfill
\DatestampYMD{2025}{05}{15} --
\DatestampYMD{2025}{12}{15}

\Entry
{\textbf{Office of Undergraduate Research}}
Chapel Hill, NC

\Gap
Research Ambassador
\hfill
\DatestampYMD{2024}{05}{15} --
\DatestampYMD{2025}{05}{15}



%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
\textbf{Programming Languages:}
MATLAB, Julia, Python, Java
\Gap
\textbf{Ocean Modeling:}
Oceananigans.jl
\Gap
\textbf{Front-end:}
\LaTeX, HTML, CSS, Markdown
\Gap
\textbf{HPC:}
Casper GPU (NCAR), Derecho (NCAR), Longleaf (UNC), Sycamore (UNC)



%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

% \Section
% {Interests}
% {Interests}
% {PDF:Interests}

% \Entry
% Digital photography,
% typography,
% swimming.


\end{Body}

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\BigGap
\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]

\end{document}
